An Improved Method for Coupling Hydrodynamics with Astrophysical Reaction Networks

### 2021-11-21 simplified_sdc_intro/paper.tex
add figure
more updates

\newcommand{\castro}{{\sf Castro}}
\newcommand{\maestro}{{\sf Maestro}}
\newcommand{\flash}{{\sf Flash}}
\newcommand{\amrex}{{\sf AMReX}}

@@

\begin{figure}[t]
\plottwo{sdc_strang_flowchart_I}{sdc_strang_flowchart_II}
\caption{\label{fig:flowchart} flowchart}
\end{figure}

@@

\subsection{Reacting Buoyant Bubble}

We next consider a buoyant, reacting bubble in a stratified,
plane-parallel atmosphere.  This test exercises the treatment of
hydrodynamical sources in the SDC integration.  We use the set of
initial conditions that was first shown in \cite{ABNZ:III}.

@@

@@

\software{\amrex\ \citep{amrex_joss},
          \castro\ \citep{castro},
          GNU Compiler Collection (\url{https://gcc.gnu.org/}),
          Linux (\url{https://www.kernel.org}),
          matplotlib (\citealt{Hunter:2007},  \url{http://matplotlib.org/})
          NumPy \citep{numpy,numpy2},
          python (\url{https://www.python.org/}), 
          SymPy \citep{sympy}
         }

>>>>

\newcommand{\castro}{{\sf Castro}}
\newcommand{\maestro}{{\sf Maestro}}
\newcommand{\pynucastro}{{\sf pynucastro}}
\newcommand{\flash}{{\sf Flash}}
\newcommand{\amrex}{{\sf AMReX}}

@@

\begin{figure}[t]
\plotone{sdc_strang_flowchart_I}
\caption{\label{fig:strang_flowchart} flowchart}
\end{figure}

\begin{figure}[t]
\plotone{sdc_strang_flowchart_II}
\caption{\label{fig:sdc_flowchart} flowchart}
\end{figure}

@@

\subsection{X-ray Burst}

We next consider a flame propagating through an accreted helium layer on a neutron star,
as described in \cite{harpole:2021}.

@@

We use a network with 28 nuclei and 96 rates that captures He burning
with links for $(\alpha,p)(p,\gamma)$ reactions and the rates
involving \isot{N}{14} to bypass
$\isotm{C}{12}(\alpha,\gamma)\isotm{O}{16}$ as described in
\cite{shenbildsten}.  The rates are taken from the ReacLib library
\citep{reaclib} and the network is written by
\pynucastro~\citep{pynucastro}.  The nuclei and links in the network are
shown in Figure~\ref{fig:subch_network}.  The many reaction pathways in this network
make it a good test for the SDC algorithm.

The initial model is generated following the procedure described in \citep{subchandra}.
For the present work, we are only concerned with the behavior of the time-integration strategy
and not on the astrophysical implications of the physical setup we explore.

\begin{figure}[t]
\centering
\plotone{subch2}
\caption{\label{fig:subch_network} Reaction network for the double detonation problem.}
\end{figure}

@@

\software{\amrex\ \citep{amrex_joss},
          \castro\ \citep{castro},
          GNU Compiler Collection (\url{https://gcc.gnu.org/}),
          Linux (\url{https://www.kernel.org}),
          matplotlib (\citealt{Hunter:2007},  \url{http://matplotlib.org/})
          NumPy \citep{numpy,numpy2},
          python (\url{https://www.python.org/}), 
          \pynucastro\ \citep{pynucastro},
          SymPy \citep{sympy}
         }
